|

### 2020-05-20 paper/Manuscript.Rmd
Fix references

Many individual researchers are motivated to adopt best practices for open
science and enjoy these benefits. And yet, the question of "how" to 
adopt open science practices can be daunting. Making the transition effectively
requires researchers to become knowledgeable about different open science 
challenges and solutions, and to become proficient with new and unfamiliar tools.
This paper is designed to ease that transition by providing a simple workflow 
that meets most requirements open science, based on best practices, and 
supported by user-friendly software in R: The Worfkflow for Open Reproducible 
Code in Science (WORCS). WORCS is a lightweight approach to open science and
computational reproducibility. The workflow (Figure \@ref(fig:workflow)) 
constitutes a step-by-step procedure that researchers can follow to make a 
research project Open and Reproducible. WORCS is compatible with open science
requirements already implemented by journals and institutions, and will help 
fulfill them. It can also be used to produce work in accordance with best 
practices in the absence of top-down support. The WORCS workflow is supported by
an R-package with user-friendly support functions, and an RStudio project
template that is, effectively, a "one click solution". This paper introduces
the WORCS workflow, discusses how it meets best practices for open science, and
illustrates the use of the `worcs` package.

@@

<!-- LB: and onwards: this section requires some background knowledge on R/packages/etc. This could be a place where readers stumble and stop reading. Perhaps introduce the concept of the R project template earlier, to see section on dependencies more into perspective. 
[main issue] it should become clear earlier what the WORCS workflow entails: e.g. switching to working with a particular R Project Template. Discuss the ‘workflow' section earlier. Related: Can you make a schematic overview of the WORCS?overview--> 
Many solutions exist to ensure computational reproducibility. These solutions typically work by
enveloping your research project in a distinct "environment" that only has access to programs that
are explicitly installed, and maintaining a record of these programs. These solutions differ in
user-friendliness and effectiveness. If strict reproducibility is required, one might use the
aforementioned Docker-based workflow by @peikertReproducibleDataAnalysis2019, which runs all
analyses inside a "container": An environment that behaves like a virtual computer that can be
stored like a sort of time capsule, and identically reinstated on a user computer, or in the cloud.
This is effective, and also preserves software outside the R environment (e.g., preprocessing tools
for neuroimaging data). However, it can be difficult to set up for novice users - although a package
is in development to facilitate this transition [@repo]. The cloud-based research collaboration platform
'Code Ocean' is also based on Docker. It is very user-friendly, but it is not clear whether the
["Data Processing Agreement"](https://www.digitalocean.com/legal/data-processing-agreement/) is fully
GDPR compliant - it seems to focus more on limiting liability than on compliance. This is a risk with
any cloud-computing solution.

@@

It is easiest to mark the distinction between essential and non-essential references from the start, instead of going
back to cut references prior to publication. Therefore, the `worcs` package distinguishes between the
traditional at-symbol (`@`) used to cite a reference, and the "double at"-symbol (`@`), used to cite a non-essential reference.
Users can render a manuscript to PDF either with, or without, comprehensive citations.

@@

1. During writing, maintain a plain-text `.bib` file with the BibTeX references for all citations.
    + You can make this file by hand; e.g., Figure \@ref(fig:scholarbib) shows how to obtain a BibTeX reference from Google Scholar; simply copy-paste each reference into the `.bib` file
    + You can export a `.bib` file from most reference manager programs; the free, open-source reference manager [Zotero](https://www.zotero.org/download/) is excellent and user-friendly, and highly interoperable with other commercial reference managers. [Here](https://christopherjunk.netlify.com/blog/2019/02/25/zotero-rmarkdown/) is a tutorial for using Zotero with Rmarkdown.
2. To cite a reference, use the `citekey` - the first word in the BibTeX entry for that reference. Insert it in the Rmarkdown file like so: `@yourcitekey2020`. For a parenthesized reference, use `[@citekeyone2020; @citekeytwo2020]`. For more options, see the [Rmarkdown cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html).
3. To indicate a *non-essential* citation, mark it with a double at-symbol: `@nonessential2020`.
4. When Knitting the document, adapt the `knit` command in the YAML header.  
  `knit: worcs::cite_all` renders all citations, and  
  `knit: worcs::cite_essential` removes all *non-essential* citations.
5. Optional: To be extremely thorough, you could make a "branch" of the GitHub repository for the print version of the manuscript. Only in this branch, you use the function `knit: worcs::cite_essential`. The procedure is documented in [this tutorial](http://rstudio-pubs-static.s3.amazonaws.com/142364_3b344a38149b465c8ebc9a8cd2eee3aa.html).

```{r scholarbib, echo = FALSE}
knitr::include_graphics("scholar_bib.png")
```

<!--
Future: Explain why each reference is cited? How best to include this?
* Note
* In a function
* In a separate document-->

>>>>

Many individual researchers are motivated to adopt best practices for open
science and enjoy these benefits. And yet, the question of "how" to 
adopt open science practices can be daunting. Making the transition effectively
requires researchers to become knowledgeable about different open science 
challenges and solutions, and to become proficient with new and unfamiliar tools.
This paper is designed to ease that transition by providing a simple workflow 
that meets most requirements open science, based on best practices, and 
supported by user-friendly software in R: The Worfkflow for Open Reproducible 
Code in Science (WORCS). WORCS is a lightweight approach to open science and
computational reproducibility. The workflow (Figure <!--\@ref(fig:workflow)-->) 
constitutes a step-by-step procedure that researchers can follow to make a 
research project Open and Reproducible. WORCS is compatible with open science
requirements already implemented by journals and institutions, and will help 
fulfill them. It can also be used to produce work in accordance with best 
practices in the absence of top-down support. The WORCS workflow is supported by
an R-package with user-friendly support functions, and an RStudio project
template that is, effectively, a "one click solution". This paper introduces
the WORCS workflow, discusses how it meets best practices for open science, and
illustrates the use of the `worcs` package.

@@

<!-- LB: and onwards: this section requires some background knowledge on R/packages/etc. This could be a place where readers stumble and stop reading. Perhaps introduce the concept of the R project template earlier, to see section on dependencies more into perspective. 
[main issue] it should become clear earlier what the WORCS workflow entails: e.g. switching to working with a particular R Project Template. Discuss the ‘workflow' section earlier. Related: Can you make a schematic overview of the WORCS?overview--> 
Many solutions exist to ensure computational reproducibility. These solutions typically work by
enveloping your research project in a distinct "environment" that only has access to programs that
are explicitly installed, and maintaining a record of these programs. These solutions differ in
user-friendliness and effectiveness. If strict reproducibility is required, one might use the
aforementioned Docker-based workflow by @peikertReproducibleDataAnalysis2019, which runs all
analyses inside a "container": An environment that behaves like a virtual computer that can be
stored like a sort of time capsule, and identically reinstated on a user computer, or in the cloud.
This is effective, and also preserves software outside the R environment (e.g., preprocessing tools
for neuroimaging data). However, it can be difficult to set up for novice users - although a package
is in development to facilitate this transition [@repro]. The cloud-based research collaboration platform
'Code Ocean' is also based on Docker. It is very user-friendly, but it is not clear whether the
["Data Processing Agreement"](https://www.digitalocean.com/legal/data-processing-agreement/) is fully
GDPR compliant - it seems to focus more on limiting liability than on compliance. This is a risk with
any cloud-computing solution.

@@

It is easiest to mark the distinction between essential and non-essential references from the start, instead of going
back to cut references prior to publication. Therefore, the `worcs` package distinguishes between the
traditional at-symbol (`@`) used to cite a reference, and the "double at"-symbol (`@@`), used to cite a non-essential reference.
Users can render a manuscript to PDF either with, or without, comprehensive citations.

@@

1. During writing, maintain a plain-text `.bib` file with the BibTeX references for all citations.
    + You can make this file by hand; e.g., Figure \@ref(fig:scholarbib) shows how to obtain a BibTeX reference from Google Scholar; simply copy-paste each reference into the `.bib` file
    + You can export a `.bib` file from most reference manager programs; the free, open-source reference manager [Zotero](https://www.zotero.org/download/) is excellent and user-friendly, and highly interoperable with other commercial reference managers. [Here](https://christopherjunk.netlify.com/blog/2019/02/25/zotero-rmarkdown/) is a tutorial for using Zotero with Rmarkdown.
2. To cite a reference, use the `citekey` - the first word in the BibTeX entry for that reference. Insert it in the Rmarkdown file like so: `@yourcitekey2020`. For a parenthesized reference, use `[@citekeyone2020; @citekeytwo2020]`. For more options, see the [Rmarkdown cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html).
3. To indicate a *non-essential* citation, mark it with a double at-symbol: `@@nonessential2020`.
4. When Knitting the document, adapt the `knit` command in the YAML header.  
  `knit: worcs::cite_all` renders all citations, and  
  `knit: worcs::cite_essential` removes all *non-essential* citations.
5. Optional: To be extremely thorough, you could make a "branch" of the GitHub repository for the print version of the manuscript. Only in this branch, you use the function `knit: worcs::cite_essential`. The procedure is documented in [this tutorial](http://rstudio-pubs-static.s3.amazonaws.com/142364_3b344a38149b465c8ebc9a8cd2eee3aa.html).

```{r, scholarbib, echo = FALSE}
knitr::include_graphics("scholar_bib.png")
```
